### 2016-06-30 R/ITHIM.Rmd
Added logNormal approximation to nonzero, non-travel MET distribution

>>>>

```{r nonZeroMETsLogNormal, echo = FALSE, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
parameters <- ddply(use[!zeroMETs,], .(sexcat, agecat2), summarise,
             mean_min = mean(minutes, na.rm=T),
             mean_mets = mean(mets, na.rm=T),
             sd_min = sd(minutes, na.rm=T),
             sd_mets = sd(mets, na.rm=T)
)
cv_mets <- with(parameters, sd_mets/mean_mets)
cv_min <- with(parameters, sd_min/mean_min)
cv0_mets<- mean(cv_mets)

mean_mets <- parameters$mean_mets
sd_mets <- cv0_mets*mean_mets

getLogNormal <- function(mu,sd){
    dlnorm(seq(0,2000,length.out=1e3), log(mu/sqrt(1+sd^2/mu^2)), sqrt(log(1+sd^2/mu^2)))
}

foo <- as.data.frame(mapply(getLogNormal, mean_mets, sd_mets))
names(foo) <- paste0(parameters$sexcat,parameters$agecat2)
foo <- melt(foo)
foo <- data.frame(foo, x = seq(0,2000,length.out = 1e3), sex = c(matrix(c("F","M"),nrow= nrow(foo)/2, ncol = 2, byrow = TRUE)), agecat = c(matrix(c("15-29","30-44","45-59","60-69","70-79", "80+"),nrow= nrow(foo)/12, ncol = 12, byrow = TRUE)))

ggplot(foo, aes(x,value, colour = agecat)) + geom_line() + facet_grid( . ~ sex) + coord_cartesian(xlim = c(0, 1500))
